---
title: "note2"
author: "yang"
date: "July 10, 2018"
output: html_document
---

# Introduction to R
## know the function
```{r}
help(mean)
args(mean)
```

## operator
### numeric
*only numeric can use numeric operator
```{r}
3 + 3 #加法
```
```{r}
3 - 3 #減法
```
```{r}
3 * 3 #乘法
```
```{r}
3 / 3 #除法，答案為小數
```
```{r}
3 %% 3 #餘數
```
### logical
####and
```{r}
c(T, T, F) & c(T, F, F)#and
c(T, T, F) && c(T, F, F)#only the first one
```
####or
```{r}
c(T, T, F) | c(T, F, F)
c(T, T, F) || c(T, F, F)#only the first one
```
####not
```{r}
!c(T, T, F)
```
####Watch out: 3 < x < 7 to check if x is between 3 and 7 will not work; you'll need 3 < x & x < 7 for that.

## condition<br />
###注意對齊及層級關係
```{r}
number = 4
if (number < 10) {
  if (number < 5) {
    result <- "extra small"
  } else {
    result <- "small"
  }
} else if (number < 100) {
  result <- "medium"
} else {
  result <- "large"
}
print(result)
```

## loops
###Indefinite Loops(while)
```{r}
i <- 1
while (i <= 10) {
  print(3*i)
  if (3*i%%8 == 0) {
    break
  }
  i <- i + 1
}
```
### Definite Loops(for)
#### version 1
```{r}
nyc <- list(pop = 8405837, 
            boroughs = c("Manhattan", "Bronx", "Brooklyn", "Queens", "Staten Island"), 
            capital = FALSE)
# Loop version 1
for (p in nyc) {
  print(p)
}
```
#### version 2
```{r}
for (i in 1:length(nyc)) {
  print(nyc[[i]])
}
```
###for loop應用
#### with matrix
```{r}
ttt <- matrix(c('O',NA,'X',NA,'O','O','X',NA,'X'), nrow = 3, byrow = T)#建構矩陣
ttt
```
```{r}
for (i in 1:nrow(ttt)) {
  for (j in 1:ncol(ttt)) {
    print(paste("On row", i ,"and column", j ,"the board contains" ,ttt[i,j]))
  }
}
```
```{r}
for (i in 1) {#只抓出第一列
  for (j in 1:ncol(ttt)) {
    print(paste("On row", i ,"and column", j ,"the board contains" ,ttt[i,j]))
  }
}
```
####抓句中字母
```{r}
rquote <- "rSTUDIO needs lots of practice!"
chars <- strsplit(rquote, split = "")[[1]]#strspilt()將句子裁切，""中放裁切條件
chars
rcount <- 0
for (char in chars) {
  if(char == 'r') {
    rcount <- rcount + 1
  }
  if(char == 'u') {
    break
  }
}
rcount
```
## variable
### type
```{r comment=""}
class(4.5)   
```
```{r}
class(3L) #Capital 'L' after an integer forces it to be stored as an integer.
class(4)
```
```{r}
class(TRUE)    
```
```{r}
class("string")
```
### operator of variable
```{r}
4.5 + 3
3.5+3L
```
```{r error = TRUE,results = "hide"}
3.5 + 'three'
```

## Vectors
### make it
```{r}
vector1 <- c(100,300,500)
vector2 <- c(200,200,-100)
vector3 <- vector1 + vector2 #向量能直接進行運算
vector3
vector4<-c(vector1,vector2)
vector4
```
### naming
#### method1
```{r comment=""}
names(vector3) <- c('America','Frances','Japan') #用names替向量命名
vector3
```
#### method2
```{r comment=""}
name<-c('America','Frances','Japan')
names(vector3)<-name
vector3
```
###operator
```{r}
#使用sum向量加總
total <- sum(vector3) 
total
```
```{r}
#使用mean計算平均值
mean <- mean(vector3) 
mean
```
### choosing
####if knowing the order:[1]注意1是第一項
```{r}
select_vec1 <- vector3[1] 
select_vec1
select_vec2 <- vector3[1:2] 
select_vec2
select_vec3 <- vector3[c(1,2)] 
select_vec3
```
#### if knowing the name: ["string"]
```{r}
select_vec4 <- vector3["America"] 
select_vec4
select_vec5 <- vector3[c("America","Frances")] 
select_vec5
```
### separate string and save<br />
```{r}
rquote<-(c("Everyday is the best day.","Isn't it?"))
strsplit(rquote, split = " ")
```
```{r}
strsplit(rquote, split = " ")[[1]]
```

## Matrix
### make it
```{r}
#星際大戰票房
new_hope <- c(460.998, 314.4)
empire_strikes <- c(290.475, 247.900)
return_jedi <- c(309.306, 165.8)
#宣告 box_office(vector)
box_office <- c(new_hope, empire_strikes, return_jedi)
#建立 star_wars_matrix
star_wars_matrix <- matrix(box_office, byrow = T, nrow = 3) 
#一個具有 3 列(narrow = 3)的矩陣，數值(box_office)依序以列(byrow = TRUE)方向填入
star_wars_matrix
```
### naming
#### method1
```{r}
#用來命名的向量 region 與 titles
region <- c("US", "non-US")
titles <- c("A New Hope", "The Empire Strikes Back", "Return of the Jedi")
#colnames()是欄命名function
colnames(star_wars_matrix) <- region
#rownames()是列命名function
rownames(star_wars_matrix) <- titles
star_wars_matrix
```
#### method2
```{r}
#dimnames()是整體命名function
dimnames(star_wars_matrix) = list(c("A New Hope", "The Empire Strikes Back", "Return of the Jedi"),c("US", "non-US"))
star_wars_matrix
```
### operator
```{r}
#rowSums()列總和(colSums()欄總和)
worldwide <- rowSums(star_wars_matrix)
worldwide
```
```{r}
#cbind()欄合併(rbind()列合併)
all_wars_matrix <- cbind(star_wars_matrix, worldwide)
all_wars_matrix
```
### choose
####使用[列,欄]，來選取
####連續選取以冒號連結
####全選留白
```{r}
#選出全部電影的美國票房收入
us_all <- all_wars_matrix[,1]
us_all
```
```{r}
#選出前兩部電影的非美國票房收入
non_us_some <- all_wars_matrix[1:2,2]
non_us_some
```

## factors
###2 kinds: nominal categorical variable  and  ordinal categorical variable
###will keep original vector
<br />
### make it
####nominal categorical variable，無法在類別之間比較好壞
```{r}
animals_vector <- c("Elephant", "Giraffe", "Donkey", "Horse")
factor_animals_vector <- factor(animals_vector)
factor_animals_vector
```
####ordinal categorical variable，天生有比較特性
```{r}
temperature_vector <- c("High", "Low", "High","Low", "Medium")
factor_temperature_vector <- factor(temperature_vector, order = TRUE, levels = c("Low", "Medium", "High"))
factor_temperature_vector
```
###naming
```{r}
survey_vector <- c("M", "F", "F", "M", "M")
factor_survey_vector <- factor(survey_vector)
factor_survey_vector
#使用levels()重新命名級別，預設以字母排序,要注意順序
levels(factor_survey_vector) <- c('Female', 'Male')
factor_survey_vector
```
```{r}
#overlook the factor，使用summary()產出摘要
#注意summary(survey_vector)結果不同，factoris better than vector
summary(survey_vector)

summary(factor_survey_vector)
```
###比大小
```{r}
#使用factor()建立順序類別
speed_vector <- c("fast", "slow", "slow", "fast", "insane")
factor_speed_vector <- factor(speed_vector, ordered = TRUE, levels = c("slow", "fast", "insane"))
factor_speed_vector
#選出資料
da2 <- factor_speed_vector[2]
da5 <- factor_speed_vector[5]
da2
da5
#資料分析師 2 是否比資料分析師 5 快？
da2 > da5
```

## dataframe<br />
### 可以儲存各種類型資料
### make it
data.frame()<br />
### choosing
```{r}
head(mtcars)#head()用來顯示dataframe的前六項
```
```{r}
tail(mtcars)#tail()用來顯示dataframe的後六項
```
```{r}
str(mtcars)#str()用來快速了解dataframe結構
```
```{r}
mtcars$qsec#選取資料框內容，以$連接欄列名稱
```
```{r}
subset(mtcars, subset = qsec > 20)#使用subset()設定篩選條件
```
```{r}
### order()重新以欄列位數值排列
mtcars[order(mtcars$qsec),]
```

## list
###can save anything
### make it
```{r}
#使用list()組合各種資料，同時分別命名
my_vector <- 1:10
my_matrix <- matrix(1:9, ncol = 3)
my_df <- mtcars[1:3,1:5]
my_list <- list(vec = my_vector, mat = my_matrix, df = my_df)
my_list
```
### naming
####method1
```{r}
names(my_list) <- c("vector", "matrix","dataframe")
my_list
```
####method2(construct and name it)
```{r}
my_list2 <- list("vector" = my_vector, "matrix" = my_matrix ,"dataframe"=my_df )
my_list2
```
### choosing
```{r}
#運用[[]]選出清單中的特定資料，再使用[]選出該指定資料的內容
my_list[["dataframe"]][2,]
```
```{r}
my_list[[1]][1]
```
```{r}
my_list$matrix
```
### add new thing
```{r}
vecme<-c(1,2,3,4,5)
ext_list <- c(my_list, "my_vvec" = vecme)
ext_list
```





## function
### introduce
```{r}
linkedin <- c(16, 9, 13, 5, NA, 17, 14)
facebook <- c(17, NA, 5, 16, 8, 13, 14)
mean(abs(linkedin - facebook),na.rm = T)#na.rm決定是否排除NA，T為排除
```
### write a function
```{r}
two_dice <- function() {
  possibilities <- 1:6
  dice1 <- sample(possibilities, size = 1)#sample()隨機選數字
  dice2 <- sample(possibilities, size = 1)
  return (dice1 + dice2)
}
two_dice()#每次的結果不同
```

### using advanced function
install.packages()<br />
```{r}
if(!require(ggplot2))install.packages("ggplot2",repos = "http://cran.us.r-project.org")
if(!require(dplyr))install.packages("dplyr",repos = "http://cran.us.r-project.org")
#install.packages("gapminder")
if(!require(gapminder))install.packages("gapminder",repos = "http://cran.us.r-project.org")
```

```{r}
library(ggplot2)
library(dplyr)
library(gapminder)

```

##applt 家族
###lapply
*lapply(list/vector, function)<br />
*Apply function over list or vector.<br />
*Always returns a list.<br />
*unlist(lapply()) to return a vector.<br />

```{r}
nyc
```
```{r}
lapply(nyc, class)
```
```{r}
unlist(lapply(nyc, class))
```
```{r}
lapply(list(1,2,3), function(x, factor) {#Using anonymous functions
  x * factor
}
, factor = 3)
```
###Sapply
*sometimes similar to unlist(lapply())<br />
```{r}
lapply(list(runif (10), runif (10)), 
       function(x) c(min = min(x), mean = mean(x), max = max(x)))
```
```{r}
sapply(list(runif (10), runif (10)), 
       function(x) c(min = min(x), mean = mean(x), max = max(x)))
```
```{r}
unlist(lapply(list(runif (10), runif (10)), 
       function(x) c(min = min(x), mean = mean(x), max = max(x))))
```
###Vapply
*vapply(list/vector, function, format)<br />
*explicitly specify output format.<br />
```{r}
#numeric(3) is the format here.
#numeric refers to classes of variables.
#'3' refers to length.
vapply(list(runif (10), runif (10)), 
       function(x) c(min = min(x), mean = mean(x), max = max(x)), numeric(3))
```
##other functions
abs(): Calculate the absolute value.<br />
sum(): Calculate the sum of all the values in a data structure.<br />
mean(): Calculate the arithmetic mean.<br />
round(): Round the values to 0 decimal places by default.<br />

seq(): Generate sequences, by specifying the from, to, and by arguments.<br />
```{r}
seq1 = seq(1, 7, by = 2)
seq1
```
rep(): Replicate elements of vectors and lists.<br />
```{r}
rep1 = rep(seq1, times = 2)
rep1
```
sort(): Sort a vector in ascending order. Works on numerics, but also on character strings and logicals.<br />
```{r}
sort1 = sort(rep1, decreasing = T)
sort1
```
rev(): Reverse the elements in a data structures for which reversal is defined.<br />
```{r}
rev1 = rev(sort1)
rev1
```
str(): Display the structure of any R object.<br />
append(): Merge vectors or lists.<br />
```{r}
append1 = append(sort1, rev1)
append1
```
is.*(): Check for the class of an R object.<br />
as.*(): Convert an R object from one class to another.<br />
unlist(): Flatten (possibly embedded) lists to produce a vector.<br />

##Regular Expressions

###Grepl & Grep
grepl(): Returns TRUE or FALSE<br />
grep(): Returns a vector of indices <br />

####^代表開頭，"@.*\\.edu$" , 代表@開始 ，".edu"結尾，其中".*"表任何字串，"\\."表真的"."
```{r}
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv", "kiara@@fakemail.edu")
hits1 =grepl(emails, pattern = '@.*\\.edu$')
hits1
hits2 =grep(emails, pattern = '@.*\\.edu$')
hits2
emails[hits1]
emails[hits2]
```
###Sub & Gsub
sub(): Specify a ‘replacement’ replace a ‘pattern’, and it only replaces the first match.
gsub(): Replaces all matches.
```{r}
#sub(pattern, replacement, object)
sub("@.*\\.edu$", "@datacamp.edu", emails)
gsub("@.*\\.edu$", "@datacamp.edu", emails)
```
```{r}
awards <- c("Won 1 Oscar.",
  "Won 1 Oscar. Another 9 wins & 24 nominations.",
  "1 win and 2 nominations.",
  "2 wins & 3 nominations.",
  "Nominated for 2 Golden Globes. 1 more win & 2 nominations.",
  "4 wins & 1 nomination.")
sub(".*\\s([0-9]+)\\snomination.*$", "\\1", awards)
gsub(".*\\s([0-9]+)\\snomination.*$", "\\1", awards)
```
##Times and Dates
1970/01/01 is the common origin for representing times and dates in programming languages.<br />
Sys.Date(): To know the date.
```{r}
str1 <- "2012-03-15"
class(str1)
date1 <- as.Date(str1, format = '%Y-%m-%d')
class(date1)
```
Sys.time(): To know the time.
```{r}
str2 <- "2012-3-12 14:23:08"
class(str2)
time2 <- as.POSIXct(str2, format = '%Y-%m-%d %H:%M:%S')
class(time2)
```
```{r}
#改變格式
format(time2, '%I:%M%p')
```
```{r}
#Calculations with Dates & Times
as.Date("2015-03-12") - as.Date("2015-02-27")
birth <- as.POSIXct("1879-03-14 14:37:23")
death <- as.POSIXct("1955-04-18 03:47:12")
einstein <- death - birth
einstein
```

##繪製圖表
### filter()
```{r}
gapminder %>%
  filter(country == 'China', year == 2002)
```
###arrange()，the gapminder itself is unchanged.
```{r}
gapminder %>%
  filter(year == 1957) %>%
  arrange(desc(pop))
```
###mutuate() ,to change & add an variable
```{r}
gapminder %>%
  filter(year == 2007) %>%
  mutate(GDP = pop * gdpPercap) %>%
  arrange(desc(GDP))
```
## Visualization
```{r}
gapminder_1952 <- gapminder %>%
  filter(year == 1952)

ggplot(gapminder_1952, aes(x = pop, y = lifeExp, color = continent, size = gdpPercap)) +
  geom_point()+
  scale_x_log10()#坐標軸以對數值表示
  expand_limits(y=0)#y軸從0開始
```
###faceting --separate graphs respectively for easier understanding.
```{r}
ggplot(gapminder_1952, aes(x = pop, y = lifeExp)) +
  geom_point() +
  scale_x_log10() +
  facet_wrap(~ continent)
```
## summarize
```{r}
by_year_continent<-gapminder %>%
  group_by(year, continent) %>%
  summarize(medianLifeExp = median(lifeExp), medianGdpPercap = median(gdpPercap))
by_year_continent
```
##Visualizing Summarized Data
```{r}
ggplot(by_year_continent, aes(x= year, y = medianGdpPercap,color = continent)) +
  geom_point() +
  expand_limits(y = 0)
```

##其他圖表
###geom_line()
```{r}
ggplot(by_year_continent, aes(x = year, y = medianGdpPercap, color = continent)) +
  geom_line() +
  expand_limits(y = 0)
```
###geom_col()
```{r}
by_continent <- gapminder %>%
  filter(year == 1952) %>%
  group_by(continent) %>%
  summarize(medianGdpPercap = median(gdpPercap))
ggplot(by_continent, aes(x = continent, y = medianGdpPercap)) +
  geom_col()
```
#geom_histogram()
```{r}
gapminder_1952 <- gapminder %>%
  filter(year == 1952)
ggplot(gapminder_1952, aes(x = pop)) +
  geom_histogram(binwidth=0.3) +
  scale_x_log10()
```
#geom_boxplot()
```{r}
#ggtitle() for adding title for the plot.
ggplot(gapminder_1952, aes(x = continent, y = gdpPercap)) +
  geom_boxplot() +
  scale_y_log10() +
  ggtitle("Comparing GDP per capita across continents")
```
