---
title: "note2"
author: "yang"
date: "July 15, 2018"
output: html_document
---
# Print bmi to the console
```{r error = TRUE,results = "hide"}
print(bmi)
```
# Check the class of bmi
```{r error = TRUE,results = "hide"}
class(bmi)
```
# Check the dimensions of bmi(row col)
```{r error = TRUE,results = "hide"}
dim(bmi)
```
# View the column names of bmi
```{r error = TRUE,results = "hide"}
names(bmi)
```
# Check the structure of bmi
```{r error = TRUE,results = "hide"}
str(bmi)
```
# Check the structure of bmi by the dplyr way
```{r error = TRUE,results = "hide"}
library(dplyr)
glimpse(bmi)
```
# View a summary of bmi
```{r error = TRUE,results = "hide"}
summary(bmi)
```
# View the first 15 rows(ordinary is 6)
```{r error = TRUE,results = "hide"}
head(bmi,15)
```
# View the last 10 rows(ordinary is 6)
```{r error = TRUE,results = "hide"}
tail(bmi,10)
```
# Histogram of BMIs from 2008
```{r error = TRUE,results = "hide"}
hist(bmi$Y2008)
```
# Scatter plot comparing BMIs from 1980 to those from 2008
```{r error = TRUE,results = "hide"}
plot(bmi$Y1980,bmi$Y2008)
```
# Turn wide data long : gather() 
```{r error = TRUE,results = "hide"}
#gather(wide_df, my_key, my_val, -col)
bmi_long <- gather(bmi, year,bmi_val, -Country)
```
# Turn long data wide: spread()
```{r error = TRUE,results = "hide"}
#spread(long_df, my_key, my_val)
bmi_wide <- spread(bmi_long, year, bmi_val)
```
# Apply separate() to bmi_cc:divide one col to two
```{r error = TRUE,results = "hide"}
bmi_cc_clean <- separate(bmi_cc, col = Country_ISO, into = c("Country", "ISO"), sep = "/")
```
# Apply unite() to bmi_cc_clean
```{r error = TRUE,results = "hide"}
bmi_cc <- unite(bmi_cc_clean, Country_ISO, Country, ISO, sep = "-")
```
# Convert characters to numerics
```{r error = TRUE,results = "hide"}
weather6 <- mutate_at(weather5, vars(CloudCover:WindDirDegrees), funs(as.numeric))
```
#string manipulation
```{r}
library(stringr)
# Trim all leading and trailing whitespace
str_trim(c("   Filip ", "Nick  ", " Jonathan"))
# Pad these strings with leading zeros
str_pad(c("23485W", "8823453Q", "994Z"),width=9,side="left",pad=0)
# Make states all uppercase 
toupper("states")
# Make to lowercase 
tolower("STATES")
#detect
str_detect(c("banana", "kiwi"), "a")
#replace
str_replace(c("banana", "kiwi"), "a", "o")
```
```{r error = TRUE,results = "hide"}
# Replace all empty strings in status with NA
social_df$status[social_df$status == ""] <- NA
# Use complete.cases() to see which rows have no missing values
complete.cases(social_df) 
# Use na.omit() to remove all rows with any missing values
na.omit(social_df)
```
# Load the dplyr package
```{r}
library(dplyr)
library(hflights)
```
