---
title: "note2"
author: "yang"
date: "July 15, 2018"
output: html_document
---
# Print bmi to the console
```{r error = TRUE,results = "hide"}
print(bmi)
```
# Check the class of bmi
```{r error = TRUE,results = "hide"}
class(bmi)
```
# Check the dimensions of bmi(row col)
```{r error = TRUE,results = "hide"}
dim(bmi)
```
# View the column names of bmi
```{r error = TRUE,results = "hide"}
names(bmi)
```
# Check the structure of bmi
```{r error = TRUE,results = "hide"}
str(bmi)
```
# Check the structure of bmi by the dplyr way
```{r error = TRUE,results = "hide"}
library(dplyr)
glimpse(bmi)
```
# View a summary of bmi
```{r error = TRUE,results = "hide"}
summary(bmi)
```
# View the first 15 rows(ordinary is 6)
```{r error = TRUE,results = "hide"}
head(bmi,15)
```
# View the last 10 rows(ordinary is 6)
```{r error = TRUE,results = "hide"}
tail(bmi,10)
```
# Histogram of BMIs from 2008
```{r error = TRUE,results = "hide"}
hist(bmi$Y2008)
```
# Scatter plot comparing BMIs from 1980 to those from 2008
```{r error = TRUE,results = "hide"}
plot(bmi$Y1980,bmi$Y2008)
```
# Turn wide data long : gather() 
```{r error = TRUE,results = "hide"}
#gather(wide_df, my_key, my_val, -col)
bmi_long <- gather(bmi, year,bmi_val, -Country)
```
# Turn long data wide: spread()
```{r error = TRUE,results = "hide"}
#spread(long_df, my_key, my_val)
bmi_wide <- spread(bmi_long, year, bmi_val)
```